### 2017-01-29 Radio/VLA_OH/VLA_2.tex
citation parentheses

% abstract:
% An exceptionally rare lensing configuration ?, providing a unique opportunity to explore the ISM conditions in this important but thus far unobservable(unexplored?unexploited?) regime of galaxy evolution. We propose to take advantage of the magnification of the lensed galaxy RXJ1131, a gas-rich merger with prodigious star formation rate of 120 \Msun yr\pmOne to search for OHM at intermediate-$z$, when the merger rate and ... . By combining this information with existing ?, we will ? These observations will ...
% inform future systematic searches of high-$z$ OHMs 
% OH maser emission at 1.67 GHz is known to be associated with regions of intense star formation within ULIRGs. As these galaxies are formed through violent mergers, studying the co-moving density of OH maser galaxies across cosmic time will allow the merger rate of the Universe to be determined in an independent way. This merger rate is an important parameter in galaxy formation and evolution scenarios.

@@

\begin{center}
{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
% Galaxy evolution and the history of galaxy mergers} 
Studying the properties of high-redshift ($z$) galaxies is crucial to understand the formation and evolution of present-day galaxies.
High-$z$ galaxies are IR-luminous due to their intense bursts 
of obscured star formation and/or their central active galactic nuclei (AGNs),
which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citet{CW13} for a review).
The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers
\citep{Riechers11a, Hayward12a, Riechers13b}, 
consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
%  merging in the hierarchical model of galaxy formation \citep{White91a}.
The merger rate is thus expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, and constraining 
its evolution allows us to track the origin and evolution of present-day populations. % emergence of current day populations.

>>>>

@@

\begin{center}
{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
% Galaxy evolution and the history of galaxy mergers}
Studying the properties of high-redshift ($z$) galaxies is crucial to understand the formation and evolution of present-day galaxies.
High-$z$ galaxies are IR-luminous due to their intense bursts
of obscured star formation and/or their central active galactic nuclei (AGNs),
which are sustained by their massive molecular gas reservoirs ($M_{\rm gas}$$>$10$^{10}$\,\Msun; see \citealt{CW13} for a review).
The gas-rich and starbursting nature of high-$z$ galaxies may be a result of galaxy mergers
\citep{Riechers11a, Hayward12a, Riechers13b},
consistent with the notion that galaxies grow through hierarchical merging \citep{White91a}.
%  merging in the hierarchical model of galaxy formation \citep{White91a}.
The merger rate is thus expected to increase towards higher redshift \citep[e.g.,][]{LeFloch05a, Magnelli09a}, and constraining
its evolution allows us to track the origin and evolution of present-day populations. % emergence of current day populations.
